Figures

### 2018-09-26 figures/02_conny_metric_key.tex
add stream/lake metric labels
better branch angle for sd
top align text labels
reletter panels
add spacing, resize subheaders
emphasize network distances

    \begin{columns} [c]     
      \begin{column}{0.4\textwidth}        
      \end{column}

@@

  % cd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}    
    \begin{column}[b]{0.4\textwidth}
      \huge{\textbf{A. Closest Lake Distance:} Network distance to the closest upstream lake.}
    \end{column}

  \begin{column}[b]{0.25\textwidth}
    \begin{tikzpicture}[scale = 2]
        \draw [-,ultra thick, cyan] (2.2,2.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);

@@

  \begin{column}[b]{0.25\textwidth}
    \begin{tikzpicture}[scale = 2]
        \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 5cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
      \end{tikzpicture}
  \end{column}
  \end{columns}

  % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[b]
    \begin{column}{0.4\textwidth}
      \huge{\textbf{C. Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
    \end{column}

@@

  % ll %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns} 
    \begin{column}[b]{0.4\textwidth}
      \huge{\textbf{B. Average Link Length:} Sum of the total length of stream reaches between junctions divided by the total number of reaches.}
    \end{column}

    \begin{column}[b]{0.25\textwidth}
      \begin{tikzpicture}[scale = 2]
        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (1.8,2.6) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);

@@

    \begin{column}[b]{0.25\textwidth}
      \begin{tikzpicture}[scale = 2]
           %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);

@@

    % sd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[b]  
    \begin{column}{0.4\textwidth}
      \huge{\textbf{D. Stream Density:} the length of all streams (minus artificial lines through lakes) divided by the area of watershed.}
    \end{column}

@@

          \draw [-,ultra thick, cyan] (2.4,3.4) to [out=290,in=40] (1.95,3);
          \draw [-,ultra thick, cyan] (0.6,3.3) to [out=40,in=190] (1,3.8);
          \draw [-,ultra thick, cyan] (1.8,4.4) to [out=290,in=70] (2.12,4);

@@

  % sr %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[b]  
    \begin{column}{0.4\textwidth}
      \huge{\textbf{E. Stream Order Ratio:} The total number of first order stream reaches divided by the total number of higher order stream reaches. In this example the lower connectivity lake has a stream order ratio of 3 whereas the higher connectivity lake has a stream order ratio of 2.}
    \end{column}

    \begin{column}{0.25\textwidth}
      \begin{tikzpicture}[scale = 2]
        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (2,3) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9);
        \draw [-, line width = 7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
        \draw [-,ultra thick, cyan] (1.8, 2.1) to [out=290,in=0] (1,1.5);

@@

    \begin{column}{0.25\textwidth}
      \begin{tikzpicture}[scale = 2]
        %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
          \draw [-, ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9);
          \draw [-,line width=7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);

>>>>

% labels
    \begin{columns}[b]     
      \begin{column}{0.4\textwidth}        
      \end{column}

@@

% spacer  
  \begin{columns}    
    \begin{column}[b]{0.4\textwidth}
      \vspace{2em}
    \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}
  \end{columns}

% lake label  
  \begin{columns}[T]    
    \begin{column}{0.4\textwidth}
      {\fontsize{65}{65}\textbf{Lake-based Metrics}}
      \vspace{3em}
    \end{column}

  \begin{column}{0.25\textwidth}
  \end{column}

  \begin{column}{0.25\textwidth}
  \end{column}
  \end{columns}

  % cd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[T]    
    \begin{column}{0.4\textwidth}
      \huge{\textbf{A. Closest Lake Distance:} Network distance to the closest upstream lake.}
    \end{column}

  \begin{column}{0.25\textwidth}
  \vspace{2em}
    \begin{tikzpicture}[scale = 2]
        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw[-,ultra thick, cyan] plot [smooth, tension = 1] coordinates {(2.2,2.8) (1.3,1.6) (-0.3,2.7) (0,0)};

@@

  \begin{column}{0.25\textwidth}
    \begin{tikzpicture}[scale = 2]
        \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 5cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
      \end{tikzpicture}
  \end{column}
  \end{columns}

% spacer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{columns}    
    \begin{column}[b]{0.4\textwidth}
    \vspace{2em}
    \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}
  \end{columns}

  % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[T]
    \begin{column}{0.4\textwidth}
      \huge{\textbf{B. Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
    \end{column}

@@

\begin{columns}    
    \begin{column}[b]{0.4\textwidth}
    \vspace{4em}
    \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}
  \end{columns}

\begin{columns}    
    \begin{column}[b]{0.4\textwidth}
      {\fontsize{65}{65}\textbf{Stream-based Metrics}}
      \vspace{2em}
    \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}
  \end{columns}

  % ll %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[T] 
    \begin{column}{0.4\textwidth}
      \huge{\textbf{C . Average Link Length:} Sum of the total length of stream reaches between junctions divided by the total number of reaches.}
    \end{column}

    \begin{column}{0.25\textwidth}
      \vspace{1em}
      \begin{tikzpicture}[scale = 2]
        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (1.8,2.6) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);

@@

    \begin{column}{0.25\textwidth}
      \vspace{-3em}
      \begin{tikzpicture}[scale = 2]
           %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);

@@

    % spacer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{columns}    
    \begin{column}[b]{0.4\textwidth}
    \vspace{2em}
    \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}
  \end{columns}

    % sd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[T]  
    \begin{column}{0.4\textwidth}
      \huge{\textbf{D. Stream Density:} the length of all streams (minus artificial lines through lakes) divided by the area of watershed.}
    \end{column}

@@

          \draw [-,ultra thick, cyan] (2.4,3.4) to [out=290,in=40] (1.95,3);
          \draw [-,ultra thick, cyan] (0.5,4.1) to [out=310,in=190] (1,3.8);
          \draw [-,ultra thick, cyan] (1.8,4.4) to [out=290,in=70] (2.12,4);

@@

  % spacer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{columns}    
    \begin{column}[b]{0.4\textwidth}
    \vspace{2em}
    \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}

  \begin{column}[b]{0.25\textwidth}
  \end{column}
  \end{columns}

  % sr %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[T]  
    \begin{column}{0.4\textwidth}
      \huge{\textbf{E. Stream Order Ratio:} The total number of first order stream reaches divided by the total number of higher order stream reaches. In this example the lower connectivity lake has a stream order ratio of 3 whereas the higher connectivity lake has a stream order ratio of 2.}
    \end{column}

    \begin{column}{0.25\textwidth}
    \vspace{1em}
      \begin{tikzpicture}[scale = 2]
        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (2,3) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9);
        \draw [-, line width = 7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
        \draw [-,ultra thick, cyan] (1.8, 2.1) to [out=290,in=0] (1,1.5);

@@

    \begin{column}{0.25\textwidth}
    \vspace{-2em}
      \begin{tikzpicture}[scale = 2]
        %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
          \draw [-, ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9);
          \draw [-,line width=7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
